---
title: "Testing mutate"
author: "Vicki Hertzberg"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First let's call up the packages we will need:

```{r}

library(RCurl); packageVersion("RCurl")
library(tidyverse); packageVersion("tidyverse")
library(stringr); packageVersion("stringr")
library(rvest); packageVersion("rvest")
library(methods); packageVersion("methods")
library(tm); packageVersion("tm")
library(wordcloud); packageVersion("wordcloud")
library(RColorBrewer); packageVersion("RColorBrewer")
library(janitor); packageVersion("janitor")
library(tidytext); packageVersion("tidytext")

```


Get the data

```{r}

url <- "https://en.wikipedia.org/wiki/List_of_songs_recorded_by_David_Bowie"
tables <- url %>% 
  read_html() %>% 
  html_nodes("table")
Bowie_songs <- tables %>%
  purrr::pluck(3) %>%
  html_table(fill = TRUE) %>%
  janitor::clean_names() %>%
  select(song, writer_s, year)
glimpse(Bowie_songs)

```

First let's clean this up a bit.

```{r}

# Clean the data

Bowie_songs <- Bowie_songs %>%
  mutate(song = gsub('\\"', "", song), year = as.numeric(year)) 

glimpse(Bowie_songs)

```

It appears that Bowie recorded 400 songs. Who wrote all of them?

```{r}

# Count the number of different songwriters
pattern <- "Bowie"
Bowie_songs$bowie_wrote <- grepl(pattern, Bowie_songs$writer_s)
sum(Bowie_songs$bowie_wrote)


```

Such a prolific writer, what was he writing about? 

First restrict to just the 337 songs for which he is a writer.

```{r}

Bowie_songs %>% filter(bowie_wrote == "TRUE") -> Bowie_songs_only

```

So what did Bowie write about?

```{r}

Bowie_songs_only %>%
  unnest_tokens(word, song) %>%
  anti_join(get_stopwords(), by = "word") %>%
  count(word, sort = TRUE) %>%
  arrange(desc(n))  -> Bowie_words

```





```{r}

Bowie_songs_only$song <- gsub(" *\\(.*?\\) *","",as.character(Bowie_songs_only$song))

Bowie_songs_only %>%
  unnest_tokens(word, song) %>%
  anti_join(get_stopwords(), by = "word") %>%
  count(word, sort = TRUE) %>%
  arrange(desc(n)) %>%
  head()

```

Another way to look at text is to create a _word cloud_, which you can think of as a multivariate histogram for words. You will be surprised, I'm sure, to learn that R has a `wordcloud` package that will allow you to create this object.


```{r}

# Create wordcloud from Bowie song titles

#We need to have the package wordcloud and RColorBrewer for this to work.
wordcloud(words = Bowie_words$word, freq = Bowie_words$n, max.words = 30, scale = c(4, 1), colors = topo.colors(n=30), random.color = TRUE)

```







```{r}

dbstring <- "David Bowie"
nchar(dbstring)
Bowie_songs %>%
  pull(writer_s) %>%
  str_subset("David Bowie") %>%
  length()

```



