---
title: "HW on text wrangling"
author: "Vicki Hertzberg"
date: "2/19/2019"
output: html_document
---
### Homework 4, due 3/6

```{r setup chunk 0, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(stringi)
```

###Section 1.

Suppose we have a vector `vText` as follows:

```{r Intro 1}
vText <- c('nurse', 'nut', 'ninja', 'nutrient', 'under', 'unusual')
```

We want to write a regular expression that matches `n`, `nu`, `un`, or `unu` in `vText` and replaces the matching patterns with `.`. To do this, the R code is as follows:

```{r}
pattern <- 'u?nu?'
gsub(pattern, '.', vText)
```

####Problem 1.

Suppose you have another vector vText as follows:

```{r Problem 1}

vText <- c("google", "logo", "dig", "blog", "boogie")

```

You want to match `g`, `og`, `go`, or `ogo` and replace with `.`.

Write the R code that will make that happen.

####Answer to Problem 1.

```{r Answer 1}

#Insert the code to answer the problem here.

```

###Section 2.

You have 3 strings of text that you wish to merge. One way to do this is to use the `paste` function.

```{r Intro 2}

x <- "I AM SAM. I AM SAM. SAM I AM."
y <- "THAT SAM-I-AM! THAT SAM-I-AM! I DO NOT LIKE THAT SAM-I-AM!"
z <- "DO YOU LIKE GREEN EGGS AND HAM?"

paste(x, y, z, collapse = NULL)


```

Extra credit: What is the difference if you use the `paste0` function instead of the `paste` function above?

####Problem 2.

Suppose that you now have 4 lines of text as follows:

```{r Problem 2}

W <- "Hey Diddle Diddle, the cat and the fiddle,"
X <- "The cow jumped over the moon."
Y <- "The little boy laughed to see such a sport,"
Z <- "And the dish ran away with the spoon."

```

Write the R code below to merge these 3 strings.

####Answer to Problem 2.

```{r Answer 2}

#Insert the code to answer the problem here.

```

###Section 3.

An alternative way to merge these text strings is to concatenate them with the `str_c` function from the `stringr` package.

Suppose we want to concatenate the 3 strings we did above, but also NA. We can do this in these two ways. What is the difference? (Answer to yourself)

```{r Intro 3}

paste(X, Y, Z, NA, collapse = NULL)
str_c(X, Y, Z, NA, collapse = NULL)

```

What is the difference between the two results? (Answer to yourself.)

####Problem 3.

We now want to concatenate our 4 vectors and NA. Do this using both methods.

```{r Problem 3}

W <- "Hey Diddle Diddle, the cat and the fiddle,"
X <- "The cow jumped over the moon."
Y <- "The little boy laughed to see such a sport,"
Z <- "And the dish ran away with the spoon."

```

####Answer to Problem 3.

```{r Answer 3}

#Insert the code to answer the problem here.

```

###Section 4.

We can use the `str_sub` function to extract parts of strings. Suppose I wanted to extract the last 5 letter of my name.

```{r Intro 4}

myName <- "Vicki Hertzberg"
Length <- str_length(myName)
last5letters <- str_sub(myName, Length-4, Length)
last5letters

```

####Problem 4. 
Suppose Melinda Higgins wants to extract the last *6* letters of her name.

```{r Problem 4}

herName <- "Melinda Higgins"

```

Write the code below to extract the last 6 letters of her name.

####Answer to Problem 4.

```{r Answer 4}

#Insert the code to answer the problem here.

```

###Section 5

Suppose I have a string and I want to split it into unique words based on the occurrence of a separator, as follows:

```{r Intro 5}

myString <- "The_quick_brown_fox_jumped_over_the_lazy_dog"

#the separator is the character "_"

mySeparatedString <- str_split(myString, "_")
mySeparatedString

```
If you look in your environment you will see that `mySeparatedString` is a List of 1.

####Problem 5.

I want to separate the following string into separate words:

```{r Problem 5}

myNewString <- "Now_is_the_time_for_all_good_men_to_come_to_the_aid_of_their_country"

```

Split this new string into separate words:

####Answer to Problem 5.

```{r Answer 5}

#Insert the code to answer the problem here.

```


###Section 6.

On another occasion, I need the same string split so that the last word comes off, and the rest remains intact. I can achieve that in the following way:

```{r Intro 6}

myString <- "The_quick_brown_fox_jumped_over_the_lazy_dog"
myNewSplitSpring <- str_split(myString, "_", n=2)
myNewSplitSpring

```

####Problem 6. 

Suppose we wanted to split off the first "word" from `myNewString`. Again, we have 

```{r Problem 6}

myNewString <- "Now_is_the_time_for_all_good_men_to_come_to_the_aid_of_their_country"

```

Split off the first word but leave the rest intact.

####Answer 6.

```{r Answer 6}

#Insert the code to answer the problem here.

```

###Section 7.

With the `stringi` package there is functionality to count the number of words in a string.

```{r Intro 7}

newString <- "The quick brown fox jumps over the lazy dog."
stri_count_words(newString)

```
####Problem 7.

```{r}

yourNewString <- "Now is the time for all good men to come to the aid of their country"

```

Use the `stri_count_words` function as above to count the number of distinct words in `yourNewString`.

####Answer 7.

```{r Answer 7}

#Insert the code to answer the problem here.

```

###Section 8.

Let's say you have a string listing famous mathematicians and you want to know if there are any duplicates in the list. You would do this as follows:

```{r Intro 8}

mathematicians <- c("Goedel", "Euler", "Gauss", "Hilbert", "Goedel", "Fermat", "LaGrange", "Gauss")
mathematicians[stri_duplicated(mathematicians)]

```

####Problem 8.

Suppose you have string listing famouse nurses and you want to find the duplicates. Here is the list:

```{r Problem 8}
nurses <-c("Nightingale", "Barton", "Dix", "Sanger", "Barton", "Woodruff", "Lincoln", "Dix", "Peplau")
```

####Answer 8.

```{r Answer 8}

#Insert your code to address the problem here

```

###Section 9.

The `LETTERS` object is a vector of length 26, consisting of all of the capital letters. Suppose we wanted to use this object to create the string`A-B_C-D_E-F_G-H_I-J_K-L_M-N_O-P_Q-R_S-T_U-V_W-X_Y-Z_`. To achieve this, we  use the following commands:

```{r Intro 9}

stri_join(LETTERS, separators = c("-","_"), collapse = "")

```

####Problem 9.

Suppose we create the object `DIGITS` as follows:

```{r Problem 9}

DIGITS <- c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9")

```

How can we form the string `0_1-2_3-4_5-6_7-8_9-'?

####Answer 9.

```{r Answer 9}

#Insert the code to solve the problem here.

```

###Section 10

Suppose we want to replace `statistician` with `mathematician` and `average` with `median` in the following pun:

```{r Intro 10}

pun <- "A statistician can have his head in an oven and his feet in ice, and he will say that on the average he feels fine"
punModified <- stri_replace_all_fixed(pun, c("statistician", "average"), c("mathematician", "median"), vectorize_all = FALSE)
punModified

```

####Problem 10

Using the original pun, replace `his` with `her` and ` he ` with ` she `:

```{r Problem 10}

pun

```

####Answer 10 

Note that the word `head` also starts with `he` but we don't want to substitute `she` into there.

```{r Answer 10}

#Insert the code to answer the problem here.

```

